FraCaS: Temporal Analysis

### 2020-10-28 paper2020/paper.tex
more correct error analysis

As it is the case for other basic phenomena, there is not much
interaction between our treatment of time and non-temporal
anaphora. One critical exception is discussed in
\cref{sec:repeatable-achievements}.

@@

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .93        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .79        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .65        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .81        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``This" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FC''
    refers to the work of \citet{bernardy_type-theoretical_2017}, and ``FC2'' its followup~\citep{bernardy_wide-coverage_2019}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with group readings}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with group readings.

We stress that group readings is already flawed in the system which we base our analysis on.
The issue is related to the difference
between narrow  and wide scope.\footnote{The literature on wide and narrow scope readings of quantifiers and quantifiers and negation is vast. We direct the reader to \cite{steedman:2012} for a comprehensive and thorough discussion of the relevant issues.} (In fact the FraCaS test suite does not appear to
test if the difference between narrow and wide scoping is handled properly.)
We propose that the situation becomes
quantitatively more difficult to handle with the added complication of
time-quantification, but not fundamentally different.

@@

\cite{bernardy_wide-coverage_2019} presented a
logical system for handling 8 of the 9 sections of the FRACAS test
suite, but excluded section 7, suggesting that it requires many
examples that require ad hoc treatment. Here, we take up this
challenge and show that a system similar to theirs can be extended to
cover the remaining section of the test suite.
%
We use the same combination of a number of well-studied tools: type
theory, parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). The system achieves an
accuracy of 0.71 on the Temporal Section and 0.78 overall.
One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with group readings and negation.

>>>>

As it is the case for other basic phenomena, there is not much
interaction between our treatment of time and non-temporal
anaphora. Critical exceptions are discussed in
\cref{sec:repeatable-achievements} and \cref{sec:interaction-with-anaphora}.

@@

\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}[hbt]
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#FraCaS
                          & This        & FC2         & FC & MINE & Nut  & LP  \\ \hline
Quantifiers  & 75         & .93        & .96         & .96    & .77  & .53  & .93  \\
             &            & \ncases{74}& \ncases{74} &        &      &      &     \ncases{44} \\
Plurals      & 33         & .79        & .82         & .76    & .67  & .52  & .73 \\
             &            &            &             &     &   &   & \ncases{24} \\
Anaphora     & 28         & .79        & .86         &   -    & -    & -    &  -       \\
Ellipsis     & 52         & .81        & .87         &   -    & -    & -    &  -       \\
Adjectives   & 22         & .95        & .95         & .95    & .68  & .32  & .73 \\
             &            & \ncases{20}&  \ncases{20}&     &   &   &  \ncases{12} \\
Comparatives & 31         & .65        & .87         & .56    & .48  & .45  &  -       \\
Temporal     & 75         & .71        &  -          &   -    &   -  &  -   &  -       \\
Verbs        & 8          & .75        & .75         &   -    & -    & -    &  -       \\
Attitudes    & 13         & .85        & .92         & .85    & .77  & .46  & .92  \\ 
             &            &            &             &        &      &      & \ncases {9}  \\ \hline
Total        & 337        & .81        & .89         & .83    & .69  & .50  & .85  \\
             &            & \ncases{329}& \ncases{259}& \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Accuracy of our system compared to others.
    ``This" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FC''
    refers to the work of \citet{bernardy_type-theoretical_2017}, and ``FC2'' its followup~\citep{bernardy_wide-coverage_2019}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} \cite{bos:2008}, and ``Langpro"
    to the system presented by \citet{abzianidze_tableau_2015}. A dash
    indicates that no attempt was made for the section. }
  \label{tab:results}
\end{table}
\paragraph{interaction with anaphora}
\label{sec:interaction-with-anaphora}
One reason explaining the lower performance of our system on some
sections of the testsuite is that our interpretation of time interacts
imperfectly with anaphora and ellipsis. Consider the following example:

\fracasex{232}
{\item	ITEL won more orders than APCOM did.
\item	APCOM won ten orders.
\hyp 	ITEL won at least eleven orders.
}

In the first premiss, our system essentially resolves the ellipsis to
get the following reading: ``ITEL won X orders and APCOM won Y orders
and X > Y.''. One would need each of the verb phrases ``won X orders''
and ``won Y orders'' to introduce their own timespans with existential
quantifiers. However, the organisation of our system is such that the
existentials are introduced before the ellipsis is
expanded. Consequently we get a wrong interpretation and the inference
cannot be made.

@@

\cite{bernardy_wide-coverage_2019} presented a
logical system for handling 8 of the 9 sections of the FRACAS test
suite, but excluded section 7, suggesting that it requires many
examples that require ad hoc treatment. Here, we take up this
challenge and show that a system similar to theirs can be extended to
cover the remaining section of the test suite.
%
We use the same combination of a number of well-studied tools: type
theory, parsing using the Grammatical Framework (GF), Monadic Dynamic
Semantics and proof assistant technology (Coq). The system achieves an
accuracy of 0.71 on the Temporal Section and 0.78 overall.
One of the
things to be looked at is fixing the issues associated with parts of
the test suite that ``broke'' when the temporal analysis was
introduced. Some of these have been already mentioned: interaction of
the temporal variables with anaphora.
